Dish: Distribution-oblivious Shell Scripting

### 2019-11-22 pldi/draft.tex
Add figs

% nv TODO: this is a hierarchy
Broadly, shell commands can be split into five major classes (summarized in Tab.~\ref{tab:classes}) with respect to their distribution characteristics, depending on how they interact with state.
These classes are ordered in ascending difficulty of distribution:
  later classes require more effort.
In this order, each class can be thought as a subset of the next one---\eg all stateless commands are pure---meaning that the synchronization mechanisms required for any superclass would work with its subclass (without seeing any performance improvements).

@@

The semantics of the language is straightforward: given a command, the
interpreter collects its options and then returns the assignment of
the first predicate that is satisfied. The final predicate is always
satisfied. For example the following two invocations of comm would be
classified as follows:

@@

\paragraph{Pure Commands}

\TODO{Complete this, giving example of sort and wc}

Even though stateless commands are a big percentage of all of them,
there are a lot of useful and popular pure commands.

@@

On the other hand, some forms of data parallelism can be exposed when
knowing the size of the input files. As mentioned in \ref{} some pure
commands (such as cat -n) only need line information to become
stateless, and knowing the size of a file could allow the system to
split it in different chunks that can be processed independently. To
account for that, edges that refer to an input resource contain the
number of lines of the file that they refer to.

@@

>>>>

% nv TODO: this is a hierarchy
Broadly, shell commands can be split into five major classes (summarized in Tab.~\ref{tab:classes}) with respect to their distribution characteristics, depending on how they interact with state.
These classes are ordered in ascending difficulty of distribution:
  later classes require more effort.
In this order, each class can be thought as a subset \kk{I am not sure this holds for all classes. I would propose saying that some classes are subsets, e.g....} of the next one---\eg all stateless commands are pure---meaning that the synchronization mechanisms required for any superclass would work with its subclass (without seeing any performance improvements).

@@

The semantics of the language is straightforward: given a command, the
interpreter collects its options and then returns the assignment of
the first predicate that is satisfied. The final predicate is always
satisfied. For example the following two invocations of \ttt{comm}
would be classified as follows:

@@

\heading{Pure Commands}
%
Together with the commands in \sta, that are always easy to
parallelize, there also exists a subclass of commands in \pur that can
be parallelized by separating them into a map and a reduce
operation. In order to allow command developers to extend \sys with
information about how to parallelize new pure commands, \sys offers an
interface to specify how to distribute a pure command.

\TODO{I am not sure a general interface is so easy to design. It needs
  more though. It might be beneficial to just talk about sort and wc
  here and how we implemented them and nothing more. Or maybe this
  could then go to the implementation? Or maybe say that one can write
  a python function that given a node of the graph, transforms it into
  many. I am not sure what is best...}

@@

\tr{On the other hand, some forms of data parallelism can be exposed
  when knowing the size of the input files. As mentioned in \ref{}
  some pure commands (such as cat -n) only need line information to
  become stateless, and knowing the size of a file could allow the
  system to split it in different chunks that can be processed
  independently. To account for that, edges that refer to an input
  resource contain the number of lines of the file that they refer
  to.}

@@

\begin{figure*}[t]
    \centering
    %% \subcaptionbox{\label{eval:minimal_grep}}{
    %%     \includegraphics[width=0.32\textwidth]{\detokenize{./figs/minimal_grep_throughput_scaleup.pdf}}
    %% }
    %% \subcaptionbox{\label{eval:grep}}{
    %%     \includegraphics[width=0.32\textwidth]{\detokenize{./figs/grep_throughput_scaleup.pdf}}
    %% }
    %% \subcaptionbox{\label{eval:minimal_sort}}{
    %%     \includegraphics[width=0.32\textwidth]{\detokenize{./figs/minimal_sort_throughput_scaleup.pdf}}
    %% }
    %% \subcaptionbox{\label{eval:topn}}{
    %%     \includegraphics[width=0.32\textwidth]{\detokenize{./figs/topn_throughput_scaleup.pdf}}
    %% }
    %% \subcaptionbox{\label{eval:wf}}{
    %%     \includegraphics[width=0.32\textwidth]{\detokenize{./figs/wf_throughput_scaleup.pdf}}
    %% }
    %% \subcaptionbox{\label{eval:spell}}{
    %%     \includegraphics[width=0.32\textwidth]{\detokenize{./figs/minimal_grep_throughput_scaleup.pdf}}
    %% }
    %% \caption{a}
    \begin{subfigure}[b]{0.32\textwidth}
        \centering
        \includegraphics[width=\textwidth]{\detokenize{./figs/minimal_grep_throughput_scaleup.pdf}}
        %% \caption{TODO}
        %% \label{eval:minimal_grep}
    \end{subfigure}%
    ~
    \begin{subfigure}[b]{0.32\textwidth}
        \centering
        \includegraphics[width=\textwidth]{\detokenize{./figs/grep_throughput_scaleup.pdf}}
        %% \caption{TODO}
        %% \label{eval:grep}
    \end{subfigure}%
    ~
    \begin{subfigure}[b]{0.32\textwidth}
        \centering
        \includegraphics[width=\textwidth]{\detokenize{./figs/minimal_sort_throughput_scaleup.pdf}}
        %% \caption{TODO}
        %% \label{eval:minimal_sort}
    \end{subfigure}%

    \begin{subfigure}[b]{0.32\textwidth}
        \centering
        \includegraphics[width=\textwidth]{\detokenize{./figs/topn_throughput_scaleup.pdf}}
        %% \caption{TODO}
        %% \label{eval:topn}
    \end{subfigure}%
    ~
    \begin{subfigure}[b]{0.32\textwidth}
        \centering
        \includegraphics[width=\textwidth]{\detokenize{./figs/wf_throughput_scaleup.pdf}}
        %% \caption{TODO}
        %% \label{eval:wf}
    \end{subfigure}%
    ~
    \begin{subfigure}[b]{0.32\textwidth}
        \centering
        \includegraphics[width=\textwidth]{\detokenize{./figs/minimal_grep_throughput_scaleup.pdf}}
        %% \caption{TODO}
        %% \label{eval:spell}
    \end{subfigure}%
    \caption{todo}
    \label{fig:microbenchmarks}
\end{figure*}
